LZ15969: Authors' Reply

### 2019-05-24 eg6-letters/incoherent/LZ15969_Hattawy_SummaryOfChanges_May23_2019.tex
update reply

\section{Summary of Changes}
Below is a summary list of the changes to the paper:

\begin{itemize}
   \item{ In response to Referee A (remove ``only''): it has been removed.}
   \item{ In response to Referee B (remove ``to ensure
the applicability of the DVCS handbag diagram''): it has been removed.}
   \item{ In response to Referee B (change ``avoid'' to ``avoids''): it has 
      been replaced.}
   \item { The figures has been edited to be within the maximum allowed length 
      3750.}

\end{itemize}

>>>>

\section{Summary of Changes}
We agree with the referees' suggestions and implemented the changes to the paper:

\begin{itemize}
   \item{ Per the recommendation of Referee A, we removed the ``only'' in the abstract.}
   \item{ Per the recommendation of Referee B, we removed ``to ensure the applicability of the DVCS handbag diagram'' and changed ``avoid'' to ``avoids'' at the end of page 3.}
   \item{ The figures have been adjusted to meet the maximum allowed length requirement.}   
\end{itemize}
